model4you reproducing: Individual treatment effect prediction for amyotrophic

### 2018-01-11 pkg/model4you/inst/reproducing_papers/2017_individual_treatment_effect_als_smmr.Rmd
simple varimp function
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1940 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: f47c6c85720b0d11aa63be84672957b5ad03ddeb

## Variable importance
```{r}
set.seed(123)
vi_alsfrs <- varimp(frst_alsfrs, 
                    risk = function(x, ...) -objfun(x, sum = TRUE, ...), 
                    nperm = 1)
var <- names(vi_alsfrs)
vi_alsfrs_d <- data.frame(variable = factor(var, levels = var[order(vi_alsfrs)]), 
                          VI = vi_alsfrs)

@@

vi_alssurv <- varimp(frst_alssurv, 
                     risk = function(x, ...) -objfun(x, sum = TRUE, ...), 
                     nperm = 1)
var <- names(vi_alssurv)
vi_alssurv_d <- data.frame(variable = factor(var, levels = var[order(vi_alssurv)]), 
                          VI = vi_alssurv)

>>>>

## Variable importance
```{r varimp}
set.seed(123)
vi_alsfrs <- varimp(frst_alsfrs)
var <- names(vi_alsfrs)
vi_alsfrs_d <- data.frame(variable = factor(var, levels = var[order(vi_alsfrs)]), 
                          VI = vi_alsfrs)

@@

vi_alssurv <- varimp(frst_alssurv)
var <- names(vi_alssurv)
vi_alssurv_d <- data.frame(variable = factor(var, levels = var[order(vi_alssurv)]), 
                          VI = vi_alssurv)
